---
title: "Anxiety Support App: Data Analysis"
author: "Your Name - Data Analyst Candidate"
date: "October 26, 2023"
output:
  html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
capture_all_output <- TRUE  # Set to FALSE for interactive use

library(tidyverse)
library(skimr)
library(here)
library(janitor)
library(patchwork)
library(knitr) # For kable

# Define output file path
project_root <- here()
data_folder <- file.path(project_root, "data")
output_folder <- file.path(project_root, "output")
plots_folder <- file.path(output_folder, "plots")

# Create output directories
if (!dir.exists(output_folder)) {
  dir.create(output_folder, recursive = TRUE) # Create parent directories if needed
}
if (!dir.exists(plots_folder)) {
  dir.create(plots_folder, recursive = TRUE)
}

output_file_path <- file.path(output_folder, "data_prep_process_analyze_log.txt") # Unified log file
data_file_path <- file.path(data_folder, "anxiety_attack_dataset.csv")

# --- Function to safely close sink connections ---
close_sinks <- function() {
    while (sink.number() > 0) {
        sink()
    }
}

# Close any existing sink connections (from previous runs)
close_sinks()
```

## 1. Introduction

This report documents the data analysis steps for the "Anxiety Support App: Marketing Audience Identification" case study.

## 2. Project Setup (From Previous Phases)

(This section is just for narrative clarity; the setup is done in the `setup` chunk)

## 3. Data Import and Preparation (From Previous Phases)

```{r prepare-process-setup, include=FALSE}
# --- Data Import and Initial Cleaning (from Prepare phase) ---
anxiety_data_raw <- read_csv(data_file_path)
anxiety_data_clean_names <- janitor::clean_names(anxiety_data_raw)

# --- Data Processing (from Process phase) ---
# Factor conversion
categorical_vars <- c("gender", "occupation", "smoking", "family_history_of_anxiety",
                     "dizziness", "medication", "recent_major_life_event")
anxiety_data_processed <- anxiety_data_clean_names %>%
  mutate(across(all_of(categorical_vars), as.factor))

# Variable creation
anxiety_data_processed <- anxiety_data_processed %>%
  mutate(high_stress = ifelse(stress_level_1_10 >= 8, 1, 0),
         high_severity = ifelse(severity_of_anxiety_attack_1_10 >= 8, 1, 0),
         untreated = ifelse(high_stress == 1 & high_severity == 1 & therapy_sessions_per_month == 0 & medication == "No", 1, 0),
         low_sleep = ifelse(sleep_hours < 7, 1, 0),
         high_alcohol = ifelse( (gender == "Female" & alcohol_consumption_drinks_week >= 8) |
                                     (gender == "Male"   & alcohol_consumption_drinks_week >= 15) |
                                     (gender == "Other" & alcohol_consumption_drinks_week >= 15)
                                   , 1, 0),
        high_caffeine = ifelse(caffeine_intake_mg_day > 400, 1, 0),
        age_group = cut(age, breaks = c(18, 30, 45, 65),
                        labels = c("18-29", "30-44", "45-64"),
                        include.lowest = TRUE))
```

## 6. Data Analysis (Analyze Phase)

```{r functions, include=FALSE}
# --- Function for Categorical Variable Visualization ---
plot_categorical <- function(data, var_name) {
  # Create frequency table
  freq_table <- table(data[[var_name]])

  # Create bar plot
  plot <- ggplot(data, aes(x = .data[[var_name]])) +
    geom_bar() +
    labs(title = paste("Distribution of", var_name),
         x = var_name,
         y = "Count") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))

  # Print to console (if capture_all_output is TRUE and sink is active)
  if (capture_all_output) {
    print(paste("Frequency Table for", var_name, ":"))
    print(freq_table)
    print(plot)
  }


  return(plot) # Return ONLY the plot object
}

# --- Function for Numeric Variable Visualization ---
plot_numeric <- function(data, var_name) {
  # Create histogram
  plot_hist <- ggplot(data, aes(x = .data[[var_name]])) +
    geom_histogram(bins = 30) +  # Adjust bins as needed
    labs(title = paste("Distribution of", var_name),
         x = var_name,
         y = "Count")

  # Create boxplot
  plot_box <- ggplot(data, aes(y = .data[[var_name]])) +
    geom_boxplot() +
    labs(title = paste("Boxplot of", var_name),
         y = var_name)

  # Print to console
  if (capture_all_output) {
        print(plot_hist)
        print(plot_box)
    }

  return(list(histogram = plot_hist, boxplot = plot_box)) #Return both plots
}
# --- Function to Combine and Save Plots ---
combine_and_save <- function(plot_list, filename, ncol = 2) {
  # Use wrap_plots with a consistent number of columns
  combined_plot <- wrap_plots(plot_list, ncol = ncol, guides = "collect")
  ggsave(filename, combined_plot, width = 12, height = 8 * (length(plot_list) / ncol), dpi = 300)
}

# --- Function for Lifestyle vs. Severity Plots ---
plot_lifestyle_vs_severity <- function(data, lifestyle_var) {
  plot <- ggplot(data, aes(x = .data[[lifestyle_var]], y = severity_of_anxiety_attack_1_10)) +
    geom_point(alpha = 0.3) +
    geom_smooth(method = "lm", se = FALSE) +
    labs(title = paste("Anxiety Severity vs.", lifestyle_var),
         x = lifestyle_var,
         y = "Severity of Anxiety Attack (1-10)")
  if (capture_all_output) { #Only print in console when capturing
        print(plot)
    }
  return(plot) # Return ONLY the plot object
}

# --- Function for Categorical Variable Comparison Plots ---
plot_categorical_comparison <- function(data, var_name) {
    plot <- ggplot(data, aes(x = factor(severity_of_anxiety_attack_1_10), fill = .data[[var_name]] )) +
        geom_bar(position = "fill") +
        labs(title = paste("Proportion of", var_name, "by Anxiety Severity"),
        x = "Severity of Anxiety Attack (1-10)",
        y = "Proportion",
        fill = var_name) +
        scale_y_continuous(labels = scales::percent)
    if (capture_all_output) { # Only print if capture_all_output is TRUE
        print(plot)
    }
    return(plot) # Return ONLY the plot object
}
```

### 6.1. Descriptive Statistics (Targeted Groups)

```{r descriptive-stats}
# --- Descriptive Statistics (Targeted Groups) ---
if (capture_all_output) {
  sink(file = output_file_path, append = TRUE, split = TRUE)
  cat("\n\n--- Descriptive Statistics (Targeted Groups) ---\n\n")
}

library(knitr) # Make sure knitr is loaded

# --- Overall Descriptive Statistics ---
cat("\nOverall Descriptive Statistics:\n")
print(kable(skim(anxiety_data_processed), format = "markdown"))


# --- High Stress Group (stress_level_1_10 >= 8) ---
cat("\nHigh Stress Group (stress_level_1_10 >= 8):\n")
high_stress_skim <- anxiety_data_processed %>%
  filter(high_stress == 1) %>%
  skim()
print(kable(high_stress_skim, format = "markdown"))

# --- High Severity Group (severity_of_anxiety_attack_1_10 >= 8) ---
cat("\nHigh Severity Group (severity_of_anxiety_attack_1_10 >= 8):\n")
high_severity_skim <- anxiety_data_processed %>%
  filter(high_severity == 1) %>%
  skim()
print(kable(high_severity_skim, format = "markdown"))


# --- Untreated Group (high_stress, high_severity, no therapy/medication) ---
cat("\nUntreated Group (High Stress, High Severity, No Therapy/Medication):\n")
untreated_skim <- anxiety_data_processed %>%
  filter(untreated == 1) %>%
  skim()
print(kable(untreated_skim, format = "markdown"))


# --- Low Sleep Group (sleep_hours < 7) ---
cat("\nLow Sleep Group (sleep_hours < 7):\n")
low_sleep_skim <- anxiety_data_processed %>%
  filter(low_sleep == 1) %>%
  skim()
print(kable(low_sleep_skim, format = "markdown"))

# --- High Alcohol Group ---
cat("\nHigh Alcohol Group:\n")
high_alcohol_skim <- anxiety_data_processed %>%
  filter(high_alcohol == 1) %>%
  skim()
print(kable(high_alcohol_skim, format = "markdown"))


# --- High Caffeine Group ---
cat("\nHigh Caffeine Group:\n")
high_caffeine_skim <- anxiety_data_processed %>%
  filter(high_caffeine == 1) %>%
  skim()
print(kable(high_caffeine_skim, format = "markdown"))

# --- Specific Statistics for Key Questions ---
# Create a data frame to store these results
key_stats <- data.frame(
  Question = character(),
  Statistic = character(),
  Value = numeric(),
  stringsAsFactors = FALSE
)

# Question 1: Percentage with severe anxiety attacks in high-stress group

q1_result <- anxiety_data_processed %>%
  filter(high_stress == 1) %>%
  summarize(percent_high_severity = mean(high_severity, na.rm = TRUE) * 100)
key_stats <- rbind(key_stats, data.frame(Question = "Q1", Statistic = "Percent High Severity (High Stress)", Value = q1_result$percent_high_severity))


# Question 3: Proportion untreated in high-stress/high-severity group

q3_result <- anxiety_data_processed %>%
  filter(high_stress == 1, high_severity == 1) %>%
  summarize(proportion_untreated = mean(untreated, na.rm = TRUE) * 100)
key_stats <- rbind(key_stats, data.frame(Question = "Q3", Statistic = "Percent Untreated (High Stress/Severity)", Value = q3_result$proportion_untreated))


# Question 8: average heart rate and breathing rate
q8_high_result <- anxiety_data_processed %>%
    filter(severity_of_anxiety_attack_1_10 >= 8) %>%
    summarise(average_heart_rate = mean(heart_rate_bpm_during_attack, na.rm = TRUE),
              average_breathing_rate = mean(breathing_rate_breaths_min, na.rm = TRUE))
key_stats <- rbind(key_stats, data.frame(Question = "Q8 (High)", Statistic = "Average Heart Rate", Value = q8_high_result$average_heart_rate))
key_stats <- rbind(key_stats, data.frame(Question = "Q8 (High)", Statistic = "Average Breathing Rate", Value = q8_high_result$average_breathing_rate))


q8_low_result <- anxiety_data_processed %>%
    filter(severity_of_anxiety_attack_1_10 < 4) %>%
    summarise(average_heart_rate = mean(heart_rate_bpm_during_attack, na.rm = TRUE),
              average_breathing_rate = mean(breathing_rate_breaths_min, na.rm = TRUE))
key_stats <- rbind(key_stats, data.frame(Question = "Q8 (Low)", Statistic = "Average Heart Rate", Value = q8_low_result$average_heart_rate))
key_stats <- rbind(key_stats, data.frame(Question = "Q8 (Low)", Statistic = "Average Breathing Rate", Value = q8_low_result$average_breathing_rate))

# Question 9: median reported severity_of_anxiety_attack_1_10 of those in therapy
q9_result <- anxiety_data_processed %>%
    filter(therapy_sessions_per_month > 0) %>%
    summarise(median_severity_with_therapy = median(severity_of_anxiety_attack_1_10, na.rm = TRUE))
key_stats <- rbind(key_stats, data.frame(Question = "Q9", Statistic = "Median Severity (With Therapy)", Value = q9_result$median_severity_with_therapy))


cat("\nKey Statistics Summary:\n")
print(kable(key_stats, format = "markdown"))


if (capture_all_output) {
  print(Sys.time())
  sink()
}
```

### 6.2. Visualizations

```{r visualizations}
# --- Visualizations ---
if (capture_all_output) {
  sink(file = output_file_path, append = TRUE, split = TRUE)
  cat("\n\n--- Visualizations ---\n\n")
}

# --- Stress Level vs. Anxiety Severity (Boxplot) ---
plot_stress_severity <- ggplot(anxiety_data_processed, aes(x = factor(high_stress), y = severity_of_anxiety_attack_1_10)) +
  geom_boxplot() +
  labs(title = "Anxiety Severity by High Stress",
       x = "High Stress (0 = No, 1 = Yes)",
       y = "Severity of Anxiety Attack (1-10)")


# --- Untreated vs. Treated (Boxplot) ---
plot_untreated_severity <- ggplot(anxiety_data_processed, aes(x = factor(untreated), y = severity_of_anxiety_attack_1_10)) +
    geom_boxplot() +
    labs(title = "Anxiety Severity by Untreated Status",
         x = "Untreated (0 = No, 1 = Yes)",
         y = "Severity of Anxiety Attack (1-10)")


# --- Lifestyle Factors vs. Anxiety Severity (Scatterplots) ---
lifestyle_vars <- c("sleep_hours", "physical_activity_hrs_week", "caffeine_intake_mg_day", "alcohol_consumption_drinks_week", "diet_quality_1_10")

lifestyle_plots <- lapply(lifestyle_vars, function(var) {
  plot_lifestyle_vs_severity(anxiety_data_processed, var)
})


# --- Age Groups vs. Anxiety Severity (within high-stress/high-severity) ---

plot_age_severity <- ggplot(anxiety_data_processed %>% filter(high_stress == 1, high_severity == 1), aes(x = age_group, y = severity_of_anxiety_attack_1_10)) +
  geom_boxplot() +
  labs(title = "Anxiety Severity by Age Group (High Stress/Severity)",
       x = "Age Group",
       y = "Severity of Anxiety Attack (1-10)")

# --- Histograms of Key Metrics, Faceted by high_stress and high_severity ---
# Heart Rate
plot_hr_facet <- ggplot(anxiety_data_processed, aes(x = heart_rate_bpm_during_attack)) +
  geom_histogram(bins = 30) +
  facet_grid(high_stress ~ high_severity) + # Facet by both
  labs(title = "Heart Rate Distribution by Stress and Severity",
       x = "Heart Rate (bpm)",
       y = "Count")


# Breathing Rate
plot_br_facet <- ggplot(anxiety_data_processed, aes(x = breathing_rate_breaths_min)) +
  geom_histogram(bins = 30) +
  facet_grid(high_stress ~ high_severity) + # Facet by both
  labs(title = "Breathing Rate Distribution by Stress and Severity",
       x = "Breathing Rate (breaths/min)",
       y = "Count")


# --- Stacked Bar Plots for Categorical Variables (Question 6)---
categorical_vars_q6 <- c("smoking", "family_history_of_anxiety", "dizziness", "recent_major_life_event")

categorical_comparison_plots <- lapply(categorical_vars_q6, function(var){
    plot_categorical_comparison(anxiety_data_processed, var)
})

# Combine and save plots
all_plots <- c(list(plot_stress_severity, plot_untreated_severity),
               lifestyle_plots,
               list(plot_age_severity, plot_hr_facet, plot_br_facet),
               categorical_comparison_plots)

combine_and_save(all_plots, file.path(plots_folder, "combined_analysis_plots.png"), ncol = 3)


if (capture_all_output) {
  print(Sys.time())
  sink()
}
```

### 6.3. Correlation Analysis

```{r correlation-analysis}
# --- Correlation Analysis ---
if (capture_all_output) {
  sink(file = output_file_path, append = TRUE, split = TRUE)
  cat("\n\n--- Correlation Analysis ---\n\n")
}

# Calculate correlations
correlations <- anxiety_data_processed %>%
  select(all_of(lifestyle_vars), severity_of_anxiety_attack_1_10) %>%
  cor(use = "pairwise.complete.obs")  # Handle potential missing values

print("Correlation Matrix:")
print(kable(correlations, format = "markdown"))

# Perform correlation tests (for statistical significance)
correlation_tests <- lapply(lifestyle_vars, function(var) {
  cor.test(anxiety_data_processed[[var]], anxiety_data_processed$severity_of_anxiety_attack_1_10)
})
names(correlation_tests) <- lifestyle_vars # Name the list elements

print("Correlation Tests:")
# Using capture.output to format the correlation test results
for (var in names(correlation_tests)) {
    cat(paste("\n*** Correlation Test for:", var, "***\n"))
    cat(capture.output(print(correlation_tests[[var]])), sep = "\n")
}


if (capture_all_output) {
  print(Sys.time())
  sink()
}
```

### 6.4. Statistical Tests (Enhanced)

```{r statistical-tests}
# --- Statistical Tests ---

if (capture_all_output) {
  sink(file = output_file_path, append = TRUE, split = TRUE)
  cat("\n\n--- Statistical Tests ---\n\n")
}

# --- T-test: Heart Rate by High Severity (with Effect Size) ---
# Question 8
t_test_hr <- t.test(heart_rate_bpm_during_attack ~ high_severity, data = anxiety_data_processed)
print("T-test: Heart Rate by High Severity")
print(t_test_hr)

# Calculate Cohen's d (effect size) for t-test
cohens_d_hr <- (mean(anxiety_data_processed$heart_rate_bpm_during_attack[anxiety_data_processed$high_severity == 1], na.rm = TRUE) -
                 mean(anxiety_data_processed$heart_rate_bpm_during_attack[anxiety_data_processed$high_severity == 0], na.rm = TRUE)) /
                sd(anxiety_data_processed$heart_rate_bpm_during_attack, na.rm = TRUE)
cat(paste("\nCohen's d for Heart Rate t-test:", cohens_d_hr, "\n"))


# --- Chi-squared Tests and Cramer's V (Question 6 and others) ---
# Function to perform chi-squared test and calculate Cramer's V
chisq_and_cramersv <- function(var1, var2) {
  tbl <- table(var1, var2)
  chi2_result <- chisq.test(tbl, correct = FALSE) # No Yates' correction

  # Calculate Cramer's V
  chi2 <- chi2_result$statistic
  n <- sum(tbl)
  k <- min(nrow(tbl), ncol(tbl))
  cramers_v <- sqrt(chi2 / (n * (k - 1)))

  cat(paste("\nChi-squared test for", deparse(substitute(var1)), "and", deparse(substitute(var2)), ":\n"))
  print(chi2_result)
  cat(paste("Cramer's V:", cramers_v, "\n"))
}

# Apply to categorical variables vs. high_severity
for (var in categorical_vars_q6) {
  chisq_and_cramersv(anxiety_data_processed[[var]], anxiety_data_processed$high_severity)
}

# --- ANOVA and Post-Hoc Tests (for multiple group comparisons) ---

# Example: ANOVA for severity_of_anxiety_attack_1_10 by occupation
cat("\nANOVA: Anxiety Severity by Occupation:\n")
anova_occupation <- aov(severity_of_anxiety_attack_1_10 ~ occupation, data = anxiety_data_processed)
print(summary(anova_occupation))

# Post-hoc test (Tukey's HSD) if ANOVA is significant
if (summary(anova_occupation)[[1]][["Pr(>F)"]][1] < 0.05) {
  cat("\nTukey's HSD Post-Hoc Test:\n")
  print(TukeyHSD(anova_occupation))
}


# Example: ANOVA for severity_of_anxiety_attack_1_10 by age_group
cat("\nANOVA: Anxiety Severity by Age Group:\n")
anova_age <- aov(severity_of_anxiety_attack_1_10 ~ age_group, data = anxiety_data_processed)
print(summary(anova_age))

if (summary(anova_age)[[1]][["Pr(>F)"]][1] < 0.05) {
  cat("\nTukey's HSD Post-Hoc Test:\n")
  print(TukeyHSD(anova_age))
}


if (capture_all_output) {
  print(Sys.time())
  sink()
}
```

### 6.5. Modeling (Optional - Enhanced)

```{r modeling}
# --- Logistic Regression Model (Optional - Enhanced) ---

if (capture_all_output) {
  sink(file = output_file_path, append = TRUE, split = TRUE)
  cat("\n\n--- Logistic Regression Model ---\n\n")
}

# Build the model (predicting high_severity), including interaction terms
model <- glm(high_severity ~ age + gender + sleep_hours + physical_activity_hrs_week +
               caffeine_intake_mg_day + alcohol_consumption_drinks_week +
               smoking + family_history_of_anxiety + stress_level_1_10 +
               dizziness + medication + therapy_sessions_per_month +
               recent_major_life_event + diet_quality_1_10 + low_sleep +
               high_alcohol + high_caffeine +
               stress_level_1_10:sleep_hours + # Interaction: stress and sleep
               stress_level_1_10:occupation,   # Interaction: stress and occupation
             data = anxiety_data_processed, family = "binomial")

# Summarize the model
summary(model)

if (capture_all_output) {
    print(Sys.time())
    sink()
}
```

### 6.6 Enhancements

```{r analyze-enhancements}
# --- Enhancements to Analyze Phase ---

if (capture_all_output) {
  sink(file = output_file_path, append = TRUE, split = TRUE)
  cat("\n\n--- Analyze Phase Enhancements ---\n\n")
}

# --- Question 2: Compare Lifestyle Factors to Overall Averages ---
cat("\nQuestion 2: Lifestyle Factor Comparisons (High Stress/Severity vs. Overall):\n")

# Calculate overall averages
overall_means <- anxiety_data_processed %>%
  summarize(across(all_of(lifestyle_vars), ~ mean(.x, na.rm = TRUE)))

# Calculate averages for high-stress/high-severity group
high_stress_severity_means <- anxiety_data_processed %>%
  filter(high_stress == 1, high_severity == 1) %>%
  summarize(across(all_of(lifestyle_vars), ~ mean(.x, na.rm = TRUE)))

# Combine and print.  Use kable for nice formatting.
comparison_table <- bind_rows(
  "Overall" = overall_means,
  "High Stress/Severity" = high_stress_severity_means,
  .id = "Group"
)
print(kable(comparison_table, format = "markdown"))


# --- Question 4: Age Group Analysis within High Stress/Severity ---
cat("\nQuestion 4: Age Group Analysis within High Stress/Severity:\n")

# Lifestyle factors by age group
lifestyle_by_age <- anxiety_data_processed %>%
  filter(high_stress == 1, high_severity == 1) %>%
  group_by(age_group) %>%
  summarize(across(all_of(lifestyle_vars), ~ mean(.x, na.rm = TRUE)))
print(kable(lifestyle_by_age, format = "markdown"))


# Treatment usage by age group
treatment_by_age <- anxiety_data_processed %>%
  filter(high_stress == 1, high_severity == 1) %>%
  group_by(age_group) %>%
  summarize(percent_therapy = mean(therapy_sessions_per_month > 0, na.rm = TRUE) * 100,
            percent_medication = mean(medication == "Yes", na.rm = TRUE) * 100)
print(kable(treatment_by_age, format = "markdown"))


# --- Question 6: High vs. Low Severity Comparisons ---
cat("\nQuestion 6: High vs. Low Severity Comparisons:\n")

# Calculate proportions for high severity
high_severity_props <- anxiety_data_processed %>%
  filter(high_severity == 1) %>%
  summarize(across(all_of(categorical_vars_q6), ~ mean(.x == "Yes", na.rm = TRUE) * 100))

# Calculate proportions for low severity
low_severity_props <- anxiety_data_processed %>%
  filter(severity_of_anxiety_attack_1_10 < 4) %>%
  summarize(across(all_of(categorical_vars_q6), ~ mean(.x == "Yes", na.rm = TRUE) * 100))

# Combine and print
comparison_table_q6 <- bind_rows(
  "High Severity" = high_severity_props,
  "Low Severity" = low_severity_props,
  .id = "Group"
)
print(kable(comparison_table_q6, format = "markdown"))

# Chi-squared tests for each variable, capturing output
for (var in categorical_vars_q6) {
    cat(paste("\nChi-squared test for", var, ":\n"))
    tbl <- table(anxiety_data_processed[[var]], anxiety_data_processed$high_severity)
    print(capture.output(chisq.test(tbl, correct = FALSE))) # Remove Yates' correction
}

if (capture_all_output) {
  print(Sys.time())
  sink()
}
```

### 6.7 Analysis Summary and Findings

Add a section to summarize all the findings from the different analysis and tie it with the questions defined in the Ask phase.

```{r analysis-summary}
# --- Analysis Summary and Findings ---
if (capture_all_output) {
  sink(file = output_file_path, append = TRUE, split = TRUE)
  cat("\n\n--- Analysis Summary and Findings ---\n\n")
}
#To be added in the next step
if (capture_all_output) {
    print(Sys.time())
    sink()
}
```

```{r close-sink, include=FALSE, eval=capture_all_output}
# Ensure sink is closed even if there's an error in a previous chunk
close_sinks()
```


