---
title: "Anxiety Support App: Data Preparation and Processing"
author: "Your Name - Data Analyst Candidate"
date: "October 26, 2023"
output:
  html_notebook
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
capture_all_output <- TRUE  # Set to FALSE for interactive use

library(tidyverse)
library(skimr)
library(here)
library(janitor)
library(patchwork)

# Define output file path
project_root <- here()
data_folder <- file.path(project_root, "data")
output_folder <- file.path(project_root, "output")
plots_folder <- file.path(output_folder, "plots")

# Create output directories
if (!dir.exists(output_folder)) {
  dir.create(output_folder)
}
if (!dir.exists(plots_folder)) {
  dir.create(plots_folder)
}

output_file_path <- file.path(output_folder, "data_prep_process_log.txt") #Updated
data_file_path <- file.path(data_folder, "anxiety_attack_dataset.csv")
```

## 1. Introduction

This report documents the data preparation and processing steps for the "Anxiety Support App: Marketing Audience Identification" case study.  The primary objective is to identify and characterize potential target audiences for the "Calm Button" application.

## 2. Project Setup and Data Acquisition

### 2.1 Loading Necessary Libraries

(Libraries are loaded in the setup chunk)

### 2.2 Defining Project Paths

(Paths are defined in the setup chunk)

### 2.3 Importing the Dataset

```{r import-data}
if (capture_all_output) {
  sink(file = output_file_path, append = TRUE, split = TRUE)
  cat("\n\n--- Importing Data ---\n\n")
}

anxiety_data_raw <- read_csv(data_file_path)

if (capture_all_output) {
  print(Sys.time())
  sink()
}
```

## 3. Detailed Data Inspection (Prepare Phase)

### 3.1 Import check

```{r import-check}
if (capture_all_output) {
  sink(file = output_file_path, append = TRUE, split = TRUE)
  cat("\n\n--- Import Check ---\n\n")
}

head(anxiety_data_raw)

if (capture_all_output) {
  print(Sys.time())
  sink()
}
```

### 3.2 Column Name Cleaning

```{r clean-names}
if (capture_all_output) {
  sink(file = output_file_path, append = TRUE, split = TRUE)
  cat("\n\n--- Column Name Cleaning ---\n\n")
}

anxiety_data_clean_names <- janitor::clean_names(anxiety_data_raw)

if (capture_all_output) {
    print(Sys.time())
  sink()
}
```

### 3.3 Data Structure

```{r data-structure}
if (capture_all_output) {
  sink(file = output_file_path, append = TRUE, split = TRUE)
  cat("\n\n--- Data Structure ---\n\n")
}

str(anxiety_data_clean_names)

if (capture_all_output) {
    print(Sys.time())
  sink()
}
```

### 3.4 Data Distribution

```{r data-summary}
if (capture_all_output) {
  sink(file = output_file_path, append = TRUE, split = TRUE)
  cat("\n\n--- Data Summary ---\n\n")
}

summary(anxiety_data_clean_names)

if (capture_all_output) {
    print(Sys.time())
  sink()
}
```

### 3.5 Further Details

```{r data-skim}
if (capture_all_output) {
  sink(file = output_file_path, append = TRUE, split = TRUE)
  cat("\n\n--- Detailed Data Summary (skimr) ---\n\n")
}

skim(anxiety_data_clean_names)

if (capture_all_output) {
    print(Sys.time())
  sink()
}
```

## 4. Detailed Variable Examination (Prepare Phase Visualizations)

```{r functions, include=FALSE}
# --- Function for Categorical Variable Visualization ---
plot_categorical <- function(data, var_name) {
  # Create frequency table
  freq_table <- table(data[[var_name]])

  # Create bar plot
  plot <- ggplot(data, aes(x = .data[[var_name]])) +
    geom_bar() +
    labs(title = paste("Distribution of", var_name),
         x = var_name,
         y = "Count") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))

  # Print to console (if capture_all_output is TRUE and sink is active)
  if (capture_all_output) {
    print(paste("Frequency Table for", var_name, ":"))
    print(freq_table)
    print(plot)
  }


  return(list(plot = plot, freq_table = freq_table)) # Return plot and table
}

# --- Function for Numeric Variable Visualization ---
plot_numeric <- function(data, var_name) {
  # Create histogram
  plot_hist <- ggplot(data, aes(x = .data[[var_name]])) +
    geom_histogram(bins = 30) +  # Adjust bins as needed
    labs(title = paste("Distribution of", var_name),
         x = var_name,
         y = "Count")

  # Create boxplot
  plot_box <- ggplot(data, aes(y = .data[[var_name]])) +
    geom_boxplot() +
    labs(title = paste("Boxplot of", var_name),
         y = var_name)

  # Print to console
  if (capture_all_output) {
    print(paste("Histogram for", var_name))
    print(plot_hist)
    print(paste("Boxplot for", var_name))
    print(plot_box)
  }

  return(list(histogram = plot_hist, boxplot = plot_box))
}

# --- Function to Combine and Save Plots ---
combine_and_save <- function(plot_list, filename, ncol = 2, type = "categorical") {
  if (type == "categorical") {
    combined_plot <- wrap_plots(plot_list, ncol = ncol, guides = "collect")

  } else {
    # Extract histograms and boxplots
    histograms <- lapply(plot_list, function(x) x$histogram)
    boxplots <- lapply(plot_list, function(x) x$boxplot)

    # Combine histograms and boxplots separately
    combined_histograms <- wrap_plots(histograms, ncol = ncol, guides = "collect")
    combined_boxplots <- wrap_plots(boxplots, ncol = ncol, guides = "collect")

    # Combine both sets of plots (histograms above boxplots)
    combined_plot <- combined_histograms / combined_boxplots # Vertical arrangement
  }

  ggsave(filename, combined_plot, width = 12, height = 8 * (length(plot_list) / 2), dpi = 300) #Adjust height
}

```

### 4.1 Categorical Variable Analysis

```{r categorical-plots}
if (capture_all_output) {
  sink(file = output_file_path, append = TRUE, split = TRUE)
  cat("\n\n--- Categorical Variable Plots ---\n\n")
}

categorical_vars <- c("gender", "occupation", "smoking", "family_history_of_anxiety",
                     "dizziness", "medication", "recent_major_life_event")

# Generate plots and tables, storing them in a list
categorical_results <- lapply(categorical_vars, function(var) {
  plot_categorical(anxiety_data_clean_names, var)
})

# Extract just the plots for combining
categorical_plots <- lapply(categorical_results, function(x) x$plot)

# Combine and save
combine_and_save(categorical_plots, file.path(plots_folder, "combined_categorical_plots.png"), type = "categorical")


if (capture_all_output) {
    print(Sys.time())
  sink()
}
```

### 4.2 Numeric Variable Analysis

```{r numeric-plots}
if (capture_all_output) {
  sink(file = output_file_path, append = TRUE, split = TRUE)
  cat("\n\n--- Numeric Variable Plots ---\n\n")
}

numeric_vars <- c("age", "sleep_hours", "physical_activity_hrs_week",
                 "caffeine_intake_mg_day", "alcohol_consumption_drinks_week",
                 "stress_level_1_10", "heart_rate_bpm_during_attack",
                 "breathing_rate_breaths_min", "sweating_level_1_5",
                 "therapy_sessions_per_month", "diet_quality_1_10",
                 "severity_of_anxiety_attack_1_10")

# Generate plots, storing them in a list
numeric_results <- lapply(numeric_vars, function(var) {
  plot_numeric(anxiety_data_clean_names, var)
})

# Combine and save numeric plots (histograms and boxplots)
combine_and_save(numeric_results, file.path(plots_folder, "combined_numeric_plots.png"), type = "numeric")


if (capture_all_output) {
  print(Sys.time())
  sink()
}
```

### 4.3 Data Type Conversion Plan

The following variables will be converted to factors in the Process phase:

*   **gender:** Categorical variable.
*   **occupation:** Categorical variable.
*   **smoking:** Categorical (Yes/No).
*   **family_history_of_anxiety:** Categorical (Yes/No).
*   **dizziness:** Categorical (Yes/No).
*   **medication:** Categorical (Yes/No).
*   **recent_major_life_event:** Categorical (Yes/No).

### 4.4 Duplicate Check

```{r duplicate-check}
if (capture_all_output) {
  sink(file = output_file_path, append = TRUE, split = TRUE)
  cat("\n\n--- Duplicate Check ---\n\n")
}

duplicates<- anxiety_data_clean_names %>%
  duplicated() %>%
  sum()
print("Number of Duplicate Rows:")
print(duplicates)

if (capture_all_output) {
    print(Sys.time())
  sink()
}
```

### 4.5 Explicit Missing Value Check

```{r missing-value-check}
if (capture_all_output) {
  sink(file = output_file_path, append = TRUE, split = TRUE)
  cat("\n\n--- Explicit Missing Value Check ---\n\n")
}

missing_values <- colSums(is.na(anxiety_data_clean_names))
print("Missing Values per Column:")
print(missing_values)

missing_percentages <- colMeans(is.na(anxiety_data_clean_names)) * 100
print("Percentage of Missing Values per Column:")
print(missing_percentages)


if (capture_all_output) {
  print(Sys.time())
  sink()
}
```

## 5. Data Processing (Process Phase)

This section details the data cleaning and transformation steps, addressing the issues and plans identified in the Prepare phase.

### 5.1 Data Type Conversion

```{r data-type-conversion}
if (capture_all_output) {
  sink(file = output_file_path, append = TRUE, split = TRUE)
  cat("\n\n--- Data Type Conversion ---\n\n")
}

# Create a copy for processing
anxiety_data_processed <- anxiety_data_clean_names

# Convert character variables to factors
categorical_vars <- c("gender", "occupation", "smoking", "family_history_of_anxiety",
                     "dizziness", "medication", "recent_major_life_event")

anxiety_data_processed <- anxiety_data_processed %>%
  mutate(across(all_of(categorical_vars), as.factor))

# Verify conversion
str(anxiety_data_processed)

if (capture_all_output) {
  print(Sys.time())
  sink()
}
```

### 5.2 Outlier Investigation and Handling

```{r outlier-handling}
if (capture_all_output) {
  sink(file = output_file_path, append = TRUE, split = TRUE)
  cat("\n\n--- Outlier Investigation and Handling ---\n\n")
}

# --- sleep_hours ---
# Investigate values < 4
low_sleep <- anxiety_data_processed %>% filter(sleep_hours < 4)
print("Observations with sleep_hours < 4:")
print(low_sleep)
# Decision: Keep.  While low, these values are plausible.

# --- physical_activity_hrs_week ---
# Investigate values > 9
high_activity <- anxiety_data_processed %>% filter(physical_activity_hrs_week > 9)
print("Observations with physical_activity_hrs_week > 9:")
print(high_activity)
# Decision: Keep. These are high but plausible values.

# --- caffeine_intake_mg_day ---
# Investigate values > 400
high_caffeine <- anxiety_data_processed %>% filter(caffeine_intake_mg_day > 400)
print("Observations with caffeine_intake_mg_day > 400:")
print(high_caffeine)
# Decision: Keep. These are high, but plausible, values.

# --- alcohol_consumption_drinks_week ---
# Investigate values > 14
high_alcohol <- anxiety_data_processed %>% filter(alcohol_consumption_drinks_week > 14)
print("Observations with alcohol_consumption_drinks_week > 14:")
print(high_alcohol)
# Decision: Keep. While above recommended limits, they are plausible.

# --- heart_rate_bpm_during_attack ---
# Investigate values < 70 and > 160
low_hr <- anxiety_data_processed %>% filter(heart_rate_bpm_during_attack < 70)
print("Observations with heart_rate_bpm_during_attack < 70:")
print(low_hr)

high_hr <- anxiety_data_processed %>% filter(heart_rate_bpm_during_attack > 160)
print("Observations with heart_rate_bpm_during_attack > 160:")
print(high_hr)
# Decision: Keep. After reviewing the context, values are kept.

# --- breathing_rate_breaths_min ---
# Investigate values < 15 and > 35
low_br <- anxiety_data_processed %>% filter(breathing_rate_breaths_min < 15)
print("Observations with breathing_rate_breaths_min < 15:")
print(low_br)
high_br <- anxiety_data_processed %>% filter(breathing_rate_breaths_min > 35)
print("Observations with breathing_rate_breaths_min > 35:")
print(high_br)
# Decision: Keep. After reviewing the context, values are kept.

if (capture_all_output) {
  print(Sys.time())
  sink()
}
```

### 5.3. Variable Creation

```{r variable-creation}
if (capture_all_output) {
    sink(file = output_file_path, append = TRUE, split = TRUE)
    cat("\n\n--- Variable Creation ---\n\n")
}

# --- High Stress Indicator ---
anxiety_data_processed <- anxiety_data_processed %>%
  mutate(high_stress = ifelse(stress_level_1_10 >= 8, 1, 0))

# --- High Severity Indicator ---
anxiety_data_processed <- anxiety_data_processed %>%
  mutate(high_severity = ifelse(severity_of_anxiety_attack_1_10 >= 8, 1, 0))

# --- Untreated Indicator ---
anxiety_data_processed <- anxiety_data_processed %>%
  mutate(untreated = ifelse(high_stress == 1 & high_severity == 1 & therapy_sessions_per_month == 0 & medication == "No", 1, 0))

# --- Low Sleep Indicator ---
anxiety_data_processed <- anxiety_data_processed %>%
      mutate(low_sleep = ifelse(sleep_hours < 7, 1, 0))


# --- High Alcohol Consumption Indicator ---
anxiety_data_processed <- anxiety_data_processed %>%
      mutate(high_alcohol = ifelse( (gender == "Female" & alcohol_consumption_drinks_week >= 8) |
                                     (gender == "Male"   & alcohol_consumption_drinks_week >= 15) |
                                     (gender == "Other" & alcohol_consumption_drinks_week >= 15)
                                   , 1, 0))

# --- High Caffeine Consumption Indicator ---
anxiety_data_processed <- anxiety_data_processed %>%
    mutate(high_caffeine = ifelse(caffeine_intake_mg_day > 400, 1, 0))

#Verify
str(anxiety_data_processed)

if (capture_all_output) {
  print(Sys.time())
  sink()
}
```

### 5.4. Verification

```{r verification}
# --- Verification ---
if (capture_all_output) {
  sink(file = output_file_path, append = TRUE, split = TRUE)
  cat("\n\n--- Verification ---\n\n")
}

# Check for NA's again in the new variables
missing_values_processed <- colSums(is.na(anxiety_data_processed))
print("Missing Values per Column After Processing:")
print(missing_values_processed)

# Check for Duplicates again
duplicates_processed <- anxiety_data_processed %>%
  duplicated() %>%
  sum()
print("Number of Duplicate Rows After Processing:")
print(duplicates_processed)

if (capture_all_output) {
  print(Sys.time())
  sink()
}
```

## 6. Data Analysis (Analyze Phase)

### 6.1. Descriptive Statistics (Targeted Groups)

```{r descriptive-stats}
# --- Descriptive Statistics (Targeted Groups) ---
if (capture_all_output) {
  sink(file = output_file_path, append = TRUE, split = TRUE)
  cat("\n\n--- Descriptive Statistics (Targeted Groups) ---\n\n")
}

library(knitr) # Make sure knitr is loaded

# --- Overall Descriptive Statistics ---
cat("\nOverall Descriptive Statistics:\n")
print(kable(skim(anxiety_data_processed), format = "markdown"))


# --- High Stress Group (stress_level_1_10 >= 8) ---
cat("\nHigh Stress Group (stress_level_1_10 >= 8):\n")
high_stress_skim <- anxiety_data_processed %>%
  filter(high_stress == 1) %>%
  skim()
print(kable(high_stress_skim, format = "markdown"))

# --- High Severity Group (severity_of_anxiety_attack_1_10 >= 8) ---
cat("\nHigh Severity Group (severity_of_anxiety_attack_1_10 >= 8):\n")
high_severity_skim <- anxiety_data_processed %>%
  filter(high_severity == 1) %>%
  skim()
print(kable(high_severity_skim, format = "markdown"))


# --- Untreated Group (high_stress, high_severity, no therapy/medication) ---
cat("\nUntreated Group (High Stress, High Severity, No Therapy/Medication):\n")
untreated_skim <- anxiety_data_processed %>%
  filter(untreated == 1) %>%
  skim()
print(kable(untreated_skim, format = "markdown"))


# --- Low Sleep Group (sleep_hours < 7) ---
cat("\nLow Sleep Group (sleep_hours < 7):\n")
low_sleep_skim <- anxiety_data_processed %>%
  filter(low_sleep == 1) %>%
  skim()
print(kable(low_sleep_skim, format = "markdown"))

# --- High Alcohol Group ---
cat("\nHigh Alcohol Group:\n")
high_alcohol_skim <- anxiety_data_processed %>%
  filter(high_alcohol == 1) %>%
  skim()
print(kable(high_alcohol_skim, format = "markdown"))


# --- High Caffeine Group ---
cat("\nHigh Caffeine Group:\n")
high_caffeine_skim <- anxiety_data_processed %>%
  filter(high_caffeine == 1) %>%
  skim()
print(kable(high_caffeine_skim, format = "markdown"))

# --- Specific Statistics for Key Questions ---
# Create a data frame to store these results
key_stats <- data.frame(
  Question = character(),
  Statistic = character(),
  Value = numeric(),
  stringsAsFactors = FALSE
)

# Question 1: Percentage with severe anxiety attacks in high-stress group

q1_result <- anxiety_data_processed %>%
  filter(high_stress == 1) %>%
  summarize(percent_high_severity = mean(high_severity) * 100)
key_stats <- rbind(key_stats, data.frame(Question = "Q1", Statistic = "Percent High Severity (High Stress)", Value = q1_result$percent_high_severity))


# Question 3: Proportion untreated in high-stress/high-severity group

q3_result <- anxiety_data_processed %>%
  filter(high_stress == 1, high_severity == 1) %>%
  summarize(proportion_untreated = mean(untreated) * 100)
key_stats <- rbind(key_stats, data.frame(Question = "Q3", Statistic = "Percent Untreated (High Stress/Severity)", Value = q3_result$proportion_untreated))


# Question 8: average heart rate and breathing rate
q8_high_result <- anxiety_data_processed %>%
    filter(severity_of_anxiety_attack_1_10 >= 8) %>%
    summarise(average_heart_rate = mean(heart_rate_bpm_during_attack),
              average_breathing_rate = mean(breathing_rate_breaths_min))
key_stats <- rbind(key_stats, data.frame(Question = "Q8 (High)", Statistic = "Average Heart Rate", Value = q8_high_result$average_heart_rate))
key_stats <- rbind(key_stats, data.frame(Question = "Q8 (High)", Statistic = "Average Breathing Rate", Value = q8_high_result$average_breathing_rate))


q8_low_result <- anxiety_data_processed %>%
    filter(severity_of_anxiety_attack_1_10 < 4) %>%
    summarise(average_heart_rate = mean(heart_rate_bpm_during_attack),
              average_breathing_rate = mean(breathing_rate_breaths_min))
key_stats <- rbind(key_stats, data.frame(Question = "Q8 (Low)", Statistic = "Average Heart Rate", Value = q8_low_result$average_heart_rate))
key_stats <- rbind(key_stats, data.frame(Question = "Q8 (Low)", Statistic = "Average Breathing Rate", Value = q8_low_result$average_breathing_rate))

# Question 9: median reported severity_of_anxiety_attack_1_10 of those in therapy
q9_result <- anxiety_data_processed %>%
    filter(therapy_sessions_per_month > 0) %>%
    summarise(median_severity_with_therapy = median(severity_of_anxiety_attack_1_10))
key_stats <- rbind(key_stats, data.frame(Question = "Q9", Statistic = "Median Severity (With Therapy)", Value = q9_result$median_severity_with_therapy))


cat("\nKey Statistics Summary:\n")
print(kable(key_stats, format = "markdown"))


if (capture_all_output) {
  print(Sys.time())
  sink()
}
```

### 6.2. Visualizations

```{r visualizations}
# --- Visualizations ---
if (capture_all_output) {
  sink(file = output_file_path, append = TRUE, split = TRUE)
  cat("\n\n--- Visualizations ---\n\n")
}

# --- Stress Level vs. Anxiety Severity (Boxplot) ---
plot_stress_severity <- ggplot(anxiety_data_processed, aes(x = factor(high_stress), y = severity_of_anxiety_attack_1_10)) +
  geom_boxplot() +
  labs(title = "Anxiety Severity by High Stress",
       x = "High Stress (0 = No, 1 = Yes)",
       y = "Severity of Anxiety Attack (1-10)")
# Keep print statement for console output
print(plot_stress_severity)

# --- Untreated vs. Treated (Boxplot) ---
plot_untreated_severity <- ggplot(anxiety_data_processed, aes(x = factor(untreated), y = severity_of_anxiety_attack_1_10)) +
    geom_boxplot() +
    labs(title = "Anxiety Severity by Untreated Status",
         x = "Untreated (0 = No, 1 = Yes)",
         y = "Severity of Anxiety Attack (1-10)")
print(plot_untreated_severity)

# --- Lifestyle Factors vs. Anxiety Severity (Scatterplots) ---

plot_lifestyle_vs_severity <- function(data, lifestyle_var) {
  plot <- ggplot(data, aes(x = .data[[lifestyle_var]], y = severity_of_anxiety_attack_1_10)) +
    geom_point(alpha = 0.3) +
    geom_smooth(method = "lm", se = FALSE) +
    labs(title = paste("Anxiety Severity vs.", lifestyle_var),
         x = lifestyle_var,
         y = "Severity of Anxiety Attack (1-10)")
  if (capture_all_output) { # Only print if capture_all_output is TRUE
        print(plot)
    }
  return(plot)
}

lifestyle_vars <- c("sleep_hours", "physical_activity_hrs_week", "caffeine_intake_mg_day", "alcohol_consumption_drinks_week", "diet_quality_1_10")

lifestyle_plots <- lapply(lifestyle_vars, function(var) {
  plot_lifestyle_vs_severity(anxiety_data_processed, var)
})


# --- Age Groups vs. Anxiety Severity (within high-stress/high-severity) ---
anxiety_data_processed <- anxiety_data_processed %>%
  mutate(age_group = cut(age, breaks = c(18, 30, 45, 65), labels = c("18-29", "30-44", "45-64"), include.lowest = TRUE))

plot_age_severity <- ggplot(anxiety_data_processed %>% filter(high_stress == 1, high_severity == 1), aes(x = age_group, y = severity_of_anxiety_attack_1_10)) +
  geom_boxplot() +
  labs(title = "Anxiety Severity by Age Group (High Stress/Severity)",
       x = "Age Group",
       y = "Severity of Anxiety Attack (1-10)")
print(plot_age_severity)
# --- Histograms of Key Metrics, Faceted by high_stress and high_severity ---

# Heart Rate
plot_hr_facet <- ggplot(anxiety_data_processed, aes(x = heart_rate_bpm_during_attack)) +
  geom_histogram(bins = 30) +
  facet_grid(high_stress ~ high_severity) +
  labs(title = "Heart Rate Distribution by Stress and Severity",
       x = "Heart Rate (bpm)",
       y = "Count")
print(plot_hr_facet)

# Breathing Rate
plot_br_facet <- ggplot(anxiety_data_processed, aes(x = breathing_rate_breaths_min)) +
  geom_histogram(bins = 30) +
  facet_grid(high_stress ~ high_severity) +
  labs(title = "Breathing Rate Distribution by Stress and Severity",
       x = "Breathing Rate (breaths/min)",
       y = "Count")
print(plot_br_facet)

# --- Stacked Bar Plots for Categorical Variables (Question 6) ---
plot_categorical_comparison <- function(data, var_name) {
    plot <- ggplot(data, aes(x = factor(severity_of_anxiety_attack_1_10), fill = .data[[var_name]] )) +
        geom_bar(position = "fill") +
        labs(title = paste("Proportion of", var_name, "by Anxiety Severity"),
        x = "Severity of Anxiety Attack (1-10)",
        y = "Proportion",
        fill = var_name) +
        scale_y_continuous(labels = scales::percent)
    if (capture_all_output) { # Only print if capture_all_output is TRUE
        print(plot)
    }
    return(plot)
}

categorical_vars_q6 <- c("smoking", "family_history_of_anxiety", "dizziness", "recent_major_life_event")

categorical_comparison_plots <- lapply(categorical_vars_q6, function(var){
    plot_categorical_comparison(anxiety_data_processed, var)
})

# Combine and save plots
all_plots <- c(list(plot_stress_severity, plot_untreated_severity),
               lifestyle_plots,
               list(plot_age_severity, plot_hr_facet, plot_br_facet),
               categorical_comparison_plots)

combine_and_save(all_plots, file.path(plots_folder, "combined_analysis_plots.png"), ncol = 3, type = "other")


if (capture_all_output) {
  print(Sys.time())
  sink()
}
```

### 6.3. Correlation Analysis

```{r correlation-analysis}
# --- Correlation Analysis ---
if (capture_all_output) {
  sink(file = output_file_path, append = TRUE, split = TRUE)
  cat("\n\n--- Correlation Analysis ---\n\n")
}

# Calculate correlations
correlations <- anxiety_data_processed %>%
  select(all_of(lifestyle_vars), severity_of_anxiety_attack_1_10) %>%
  cor(use = "pairwise.complete.obs")  # Handle potential missing values (though we have none)

print("Correlation Matrix:")
print(kable(correlations, format = "markdown"))

# Perform correlation tests (for statistical significance)
correlation_tests <- lapply(lifestyle_vars, function(var) {
  cor.test(anxiety_data_processed[[var]], anxiety_data_processed$severity_of_anxiety_attack_1_10)
})
names(correlation_tests) <- lifestyle_vars # Name the list elements

print("Correlation Tests:")
# Using capture.output to format the correlation test results
for (var in names(correlation_tests)) {
    cat(paste("\n*** Correlation Test for:", var, "***\n"))
    cat(capture.output(print(correlation_tests[[var]])), sep = "\n")
}


if (capture_all_output) {
  print(Sys.time())
  sink()
}
```

### 6.4. Statistical Tests (Optional)

```{r statistical-tests}
# --- Statistical Tests ---

if (capture_all_output) {
  sink(file = output_file_path, append = TRUE, split = TRUE)
  cat("\n\n--- Statistical Tests ---\n\n")
}

# --- T-test: Heart Rate by High Severity ---
# Question 8
t_test_hr <- t.test(heart_rate_bpm_during_attack ~ high_severity, data = anxiety_data_processed)
print("T-test: Heart Rate by High Severity")
print(t_test_hr)


# --- Chi-squared Test: Smoking by High Severity ---
# Question 6
chisq_test_smoking <- chisq.test(anxiety_data_processed$smoking, anxiety_data_processed$high_severity)
print("Chi-squared Test: Smoking by High Severity")
print(chisq_test_smoking)

if (capture_all_output) {
    print(Sys.time())
    sink()
}
```

### 6.5. Modeling (Optional)

```{r modeling}
# --- Logistic Regression Model (Optional) ---

if (capture_all_output) {
  sink(file = output_file_path, append = TRUE, split = TRUE)
  cat("\n\n--- Logistic Regression Model ---\n\n")
}

# Build the model (predicting high_severity)
model <- glm(high_severity ~ age + gender + sleep_hours + physical_activity_hrs_week +
               caffeine_intake_mg_day + alcohol_consumption_drinks_week +
               smoking + family_history_of_anxiety + stress_level_1_10 +
               dizziness + medication + therapy_sessions_per_month +
               recent_major_life_event + diet_quality_1_10 + low_sleep + high_alcohol + high_caffeine,
             data = anxiety_data_processed, family = "binomial")

# Summarize the model
summary(model)

if (capture_all_output) {
    print(Sys.time())
    sink()
}
```

### 6.6 Enhancements

```{r analyze-enhancements}
# --- Enhancements to Analyze Phase ---

if (capture_all_output) {
  sink(file = output_file_path, append = TRUE, split = TRUE)
  cat("\n\n--- Analyze Phase Enhancements ---\n\n")
}

# --- Question 2: Compare Lifestyle Factors to Overall Averages ---
cat("\nQuestion 2: Lifestyle Factor Comparisons (High Stress/Severity vs. Overall):\n")

# Calculate overall averages
overall_means <- anxiety_data_processed %>%
  summarize(across(all_of(lifestyle_vars), ~ mean(.x, na.rm = TRUE)))

# Calculate averages for high-stress/high-severity group
high_stress_severity_means <- anxiety_data_processed %>%
  filter(high_stress == 1, high_severity == 1) %>%
  summarize(across(all_of(lifestyle_vars), ~ mean(.x, na.rm = TRUE)))

# Combine and print.  Use kable for nice formatting.
comparison_table <- bind_rows(
  "Overall" = overall_means,
  "High Stress/Severity" = high_stress_severity_means,
  .id = "Group"
)
print(kable(comparison_table, format = "markdown"))


# --- Question 4: Age Group Analysis within High Stress/Severity ---
cat("\nQuestion 4: Age Group Analysis within High Stress/Severity:\n")

# Lifestyle factors by age group
lifestyle_by_age <- anxiety_data_processed %>%
  filter(high_stress == 1, high_severity == 1) %>%
  group_by(age_group) %>%
  summarize(across(all_of(lifestyle_vars), ~ mean(.x, na.rm = TRUE)))
print(kable(lifestyle_by_age, format = "markdown"))


# Treatment usage by age group
treatment_by_age <- anxiety_data_processed %>%
  filter(high_stress == 1, high_severity == 1) %>%
  group_by(age_group) %>%
  summarize(percent_therapy = mean(therapy_sessions_per_month > 0) * 100,
            percent_medication = mean(medication == "Yes") * 100)
print(kable(treatment_by_age, format = "markdown"))


# --- Question 6: High vs. Low Severity Comparisons ---
cat("\nQuestion 6: High vs. Low Severity Comparisons:\n")

# Calculate proportions for high severity
high_severity_props <- anxiety_data_processed %>%
  filter(high_severity == 1) %>%
  summarize(across(all_of(categorical_vars_q6), ~ mean(.x == "Yes") * 100))

# Calculate proportions for low severity
low_severity_props <- anxiety_data_processed %>%
  filter(severity_of_anxiety_attack_1_10 < 4) %>%
  summarize(across(all_of(categorical_vars_q6), ~ mean(.x == "Yes") * 100))

# Combine and print
comparison_table_q6 <- bind_rows(
  "High Severity" = high_severity_props,
  "Low Severity" = low_severity_props,
  .id = "Group"
)
print(kable(comparison_table_q6, format = "markdown"))

# Chi-squared tests for each variable, capturing output
for (var in categorical_vars_q6) {
    cat(paste("\nChi-squared test for", var, ":\n"))
    tbl <- table(anxiety_data_processed[[var]], anxiety_data_processed$high_severity)
    print(capture.output(chisq.test(tbl)))
}

if (capture_all_output) {
  print(Sys.time())
  sink()
}
```

### 6.7 Analysis Summary and Findings

Add a section to summarize all the findings from the different analysis and tie it with the questions defined in the Ask phase.

```{r analysis-summary}
# --- Analysis Summary and Findings ---
if (capture_all_output) {
  sink(file = output_file_path, append = TRUE, split = TRUE)
  cat("\n\n--- Analysis Summary and Findings ---\n\n")
}
#To be added in the next step
if (capture_all_output) {
    print(Sys.time())
    sink()
}
```

```{r close-sink, include=FALSE, eval=capture_all_output}
# Ensure sink is closed even if there's an error in a previous chunk
if (sink.number() > 0) {
    print(Sys.time())
  sink()
}
```


